---
title: "FuncionesRST"
author: "Ricardo Morales"
date: "2023-03-30"
output: html_document
---

# FuncionesRST: a demo package

## This is a demo package from R4DS tutorial

***Any contact suggestion to the following email "[angel.morales\@est.ikiam.edu.ec](mailto:angel.morales@est.ikiam.edu.ec){.email}"***

## Installation and loading

Install the latest version from [GitHub] (<https://github.com/RicardoMorales2001/FuncionesRST>) as follow:

## Installing RStudio and the RST Functions package

The following code will help to download the devtools package which will help in downloading the RST Functions library

```{r message=FALSE, warning=FALSE}
if(!require(devtools)) install.packages("devtools")
```

Subsequently, the following code will be used to download this package

```{r message=FALSE, warning=FALSE}
devtools::install_github("https://github.com/RicardoMorales2001/FuncionesRST")
```

Once this process is done we will be able to use the functions loaded in said package.

***Note: if it is your first time working in the RStudio environment, I will leave you with a series of tutorials in Spanish which will guide you in installing the same R and RStudio program, as well as downloading packages and libraries.***

Here is a tutorial which can help you install the RStudio program in case you do not have it installed, this video is courtesy of the Sean Reyes channel

<iframe width="560" height="315" src="https://www.youtube.com/embed/nVrm5Jf1dPk" title="YouTube video player" frameborder="0" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; web-share" allowfullscreen>

</iframe>

Tutorial to download packages and libraries courtesy of the channel Rafa Gonzalez Gouveia.

<iframe width="560" height="315" src="https://www.youtube.com/embed/Bay9FTIJaiY" title="YouTube video player" frameborder="0" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; web-share" allowfullscreen>

</iframe>
